### 2021-01-24 paper/arm.tex
downgrade
x
edits

\begin{definition}
  \label{def:DS}
  Let $[\FALSE/\D]$ be the substitution that performs $[\FALSE/\Dx{\aLoc}]$
  for every $\aLoc$.
  Let $\DS{\aLoc}{\amode}$ and $\DL{\aLoc}{\amode}$ be defined:
  \begin{align*}
    \DS{\aLoc}{\mRLX}{\bForm}&=\bForm[\TRUE/\Dx{\aLoc}] 
    &\DL{\aLoc}{\mRLX}&=\TRUE
    \\
    \DS{\aLoc}{\mRA}{\bForm}&=\bForm[\FALSE/\D]
    &\DL{\aLoc}{\mRA}&=\Dx{\aLoc}
    \\
    \DS{\aLoc}{\mSC}{\bForm}&=\bForm[\FALSE/\D]
    &\DL{\aLoc}{\mSC}&=\Dx{\aLoc}
  \end{align*}
\end{definition}

\begin{definition}[$\xCO$/$\xRASC$/$\xDGR$]
  \label{def:pomsets-down}
  Update \refdef{def:pomsets-ra} to:
  \begin{enumerate}
  \item[\ref{S4})]
    $\aTr{\bEvs}{\bForm}$ implies $(\Qw{\aLoc}\limplies\aExp{\neq}\aVal)\land \DS{\aLoc}{\amode}\bForm\noSUB{[\aExp/\aLoc]}$,
  \item[\ref{S5})]
    $\aTr{\cEvs}{\bForm}$ implies $\lnot\Qw{\aLoc}\land \DS{\aLoc}{\amode}\bForm\noSUB{[\aExp/\aLoc]}$.
  \item[\ref{L5})]
    % $\aTr{\cEvs}{\bForm}$ implies $\lnot\Qx{\aLoc} \land \DL{\aLoc}{\amode} \land((\aVal{=}\aReg\lor\aLoc{=}\aReg)\limplies\bForm)$,
    % \item[\ref{L6})]
    $\aTr{\dEvs}{\bForm}$ implies $\lnot\Qx{\aLoc} \land \DL{\aLoc}{\amode} \land\bForm$.
  \end{enumerate}
\end{definition}

\begin{example}
  Revisiting \refex{ex:dgr1}.
  \begin{gather*}
    \hbox{\begin{tikzinline}[node distance=1.5em]
        \event{a}{\DW{x}{2}}{}
        \raevent{b}{\DR[\mRA]{x}{2}}{right=of a}
        \event{c}{\DW{y}{1}}{right=of b}
        \event{d}{\DW{y}{2}}{right=2.5em of c}
        \raevent{e}{\DW[\mRA]{x}{1}}{right=of d}
        \rf{a}{b}
        % \sync{b}{c}
        \wk{c}{d}
        \sync{d}{e}
        \wk[out=-165,in=-15]{e}{a}
      \end{tikzinline}}  
  \end{gather*}  
\end{example}

@@

\begin{example}
  Revisiting \refex{ex:rrd1}
  \begin{align*}
    \begin{gathered}
      r\GETS y
      \\[-.4ex]
      \hbox{\begin{tikzinline}[node distance=0.5em and 1.5em]
          \event{a}{\DR{y}{1}}{}
          \xform{xd}{1{=}r\limplies\bForm}{below=of a}
          \xform{xi}{(y{=}r\lor1{=}r)\limplies\bForm}{below=of xd}
          \xo{a}{xd}
        \end{tikzinline}}
    \end{gathered}
    &&
    \begin{gathered}
      \IF{r}\THEN s\GETS x\FI
      \\[-.4ex]
      \hbox{\begin{tikzinline}[node distance=0.5em and 1.5em]
          \event{b}{r\mid\DR{x}{0}}{}
        \end{tikzinline}}
    \end{gathered}
  \end{align*}
\end{example}

@@

\begin{definition}[$\xCO$/$\xRASC$/$\xDGR$/$\xRRD$]
  \label{def:pomsets-arm}
  Update \refdef{def:pomsets-trans} to:
  \begin{enumerate}
  \item[\ref{S3})]
    $\labelingForm(\aEv)$ implies $\QS{\aLoc}{\amode}\land\aExp{=}\aVal$,
  \item[\ref{L3})]
    $\labelingForm(\aEv)$ implies $\QL{\aLoc}{\amode}$.
  \item[\ref{T3})]
    $\labelingForm(\aEv)$ implies
    $\labelingForm_1(\aEv)[\TRUE/\Q{}][\TRUE/\RW]$ if $\labelingAct_1(\aEv)$ is a write,
    \\
    $\labelingForm(\aEv)$ implies
    $\labelingForm_1(\aEv)[\TRUE/\Q{}][\FALSE/\RW]$ otherwise.
  \end{enumerate}
  \begin{enumerate}
  \item[\ref{S4})]
    $\aTr{\bEvs}{\bForm}$ implies $(\Qw{\aLoc}\limplies\aExp{\neq}\aVal)\land \DS{\aLoc}{\amode}\bForm\noSUB{[\aExp/\aLoc]}$,
  \item[\ref{S5})]
    $\aTr{\cEvs}{\bForm}$ implies $\lnot\Qw{\aLoc}\land \DS{\aLoc}{\amode}\bForm\noSUB{[\aExp/\aLoc]}$.
  \item[\ref{L4})]
    $\aTr{\bEvs}{\bForm}$ implies $\aVal{=}\aReg\limplies\bForm$, 
  \item[\ref{L5})]
    % $\aTr{\cEvs}{\bForm}$ implies $\lnot\Qx{\aLoc} \land \DL{\aLoc}{\amode} \land(\RW\limplies(\aVal{=}\aReg\lor\aLoc{=}\aReg)\limplies\bForm)$,
    % \item[\ref{L6})]
    $\aTr{\cEvs}{\bForm}$ implies $\lnot\Qx{\aLoc} \land \DL{\aLoc}{\amode}
    \land (\RW\limplies\bForm)$.
  \end{enumerate}  
\end{definition}

>>>>

\begin{definition}
  \label{def:DS}
  Let $[\FALSE/\D]$ be the substitution that performs $[\FALSE/\Dx{\aLoc}]$
  for every $\aLoc$.
  Let $\DS{\aLoc}{\amode}{}$ and $\DL{\aLoc}{\amode}{}$ be defined:
  \begin{align*}
    \DS{\aLoc}{\mRLX}{\bForm}&=\bForm[\TRUE/\Dx{\aLoc}] 
    &\DL{\aLoc}{\mRLX}{\bForm}&=\bForm%\TRUE
    \\
    \DS{\aLoc}{\mRA}{\bForm}&=\bForm[\FALSE/\D]
    &\DL{\aLoc}{\mRA}{\bForm}&=\bForm\land\Dx{\aLoc}
    \\
    \DS{\aLoc}{\mSC}{\bForm}&=\bForm[\FALSE/\D]
    &\DL{\aLoc}{\mSC}{\bForm}&=\bForm\land\Dx{\aLoc}
  \end{align*}
\end{definition}

\begin{definition}[$\xCO$/$\xRASC$/$\xDGR$]
  \label{def:pomsets-down}
  Update \refdef{def:pomsets-ra} to:
  \begin{enumerate}
  % \item[\ref{S4})]
  %   $\aTr{\bEvs}{\bForm}$ implies $(\Qw{\aLoc}\limplies\aExp{\neq}\aVal)\land \DS{\aLoc}{\amode}\bForm\noSUB{[\aExp/\aLoc]}$,
  % \item[\ref{S5})]
  %   $\aTr{\cEvs}{\bForm}$ implies $\lnot\Qw{\aLoc}\land \DS{\aLoc}{\amode}\bForm\noSUB{[\aExp/\aLoc]}$.
  % \item[\ref{L5})]
  %   % $\aTr{\cEvs}{\bForm}$ implies $\lnot\Qx{\aLoc} \land \DL{\aLoc}{\amode}{} \land((\aVal{=}\aReg\lor\aLoc{=}\aReg)\limplies\bForm)$,
  %   % \item[\ref{L6})]
  %   $\aTr{\dEvs}{\bForm}$ implies $\lnot\Qx{\aLoc} \land \DL{\aLoc}{\amode}{} \land\bForm$.
  \item[\ref{S4})]
    $\aTr{\bEvs}{\bForm}$ implies $\DS{\aLoc}{\amode}{\bForm[(\Qw{\aLoc}\land\aExp{=}\aVal)/\Qw{\aLoc}]}$,
  \item[\ref{S5})]
    $\aTr{\cEvs}{\bForm}$ implies $\DS{\aLoc}{\amode}{\bForm[\FALSE/\Qw{\aLoc}]}$.
  \item[\ref{L5})]
    $\aTr{\dEvs}{\bForm}$ implies $\DL{\aLoc}{\amode}{\bForm[\FALSE/\Qx{\aLoc}]}$.
  \end{enumerate}
\end{definition}

\begin{example}
  Revisiting \refex{ex:dgr1} and eliding irrelevant transformers:
  \begin{align*}
    \begin{gathered}[t]
      \PW{x}{2}
      \\
      \hbox{\begin{tikzinline}[node distance=0.5em and 1.5em]
          \event{a}{\DW{x}{2}}{}
          \xform{x1d}{\bForm[\TRUE/\Dx{\aLoc}]}{below=of a}
          % \xform{x1i}{\lnot\Qw{x}\land\bForm[\TRUE/\Dx{x}]}{below=of x1d}
          \xo{a}{x1d}
        \end{tikzinline}}  
    \end{gathered}  
    &&
    \begin{gathered}[t]
      \PR[\mRA]{x}{r}
      \\
      \hbox{\begin{tikzinline}[node distance=0.5em and 1.5em]
          \raevent{b}{\DR[\mRA]{x}{2}}{}
          % \xform{x1d}{2{=}r\limplies\bForm}{below=of b}
          \xform{x1i}{\Dx{x} \land\bForm[\FALSE/\Qx{x}]}{below=of b} %x1d}
          % \xo{b}{x1d}
        \end{tikzinline}}  
    \end{gathered}  
    &&
    \begin{gathered}[t]
      \PW{y}{1}
      \\
      \hbox{\begin{tikzinline}[node distance=0.5em and 1.5em]
          \event{c}{\DW{y}{1}}{}
          % \xform{x1d}{\bForm[\TRUE/\Dx{\aLoc}]}{below=of c}
          % \xform{x1i}{\lnot\Qw{y}\land\bForm[\TRUE/\Dx{y}]}{below=of x1d}
          % \xo{c}{x1d}
        \end{tikzinline}}  
    \end{gathered}  
  \end{align*}
  Associating right:
  \begin{align*}
    \begin{gathered}[t]
      \PW{x}{2}
      \\
      \hbox{\begin{tikzinline}[node distance=0.5em and 1.5em]
          \event{a}{\DW{x}{2}}{}
          \xform{x1d}{\bForm[\TRUE/\Dx{\aLoc}]}{right=.7em of a}
          % \xform{x1i}{\lnot\Qw{x}\land\bForm[\TRUE/\Dx{x}]}{below=of x1d}
          \xo{a}{x1d}
        \end{tikzinline}}  
    \end{gathered}  
    &&
    \begin{gathered}[t]
      \PR[\mRA]{x}{r}
      \SEMI
      \PW{y}{1}
      \\
      \hbox{\begin{tikzinline}[node distance=0.5em and 1.5em]
          \raevent{b}{\DR[\mRA]{x}{2}}{}
          \event{c}{\Dx{x}\mid\DW{y}{1}}{right=.7em of b}
        \end{tikzinline}}  
    \end{gathered}  
  \end{align*}
  Composing, we have, as desired:
  \begin{align*}
    \begin{gathered}[t]
      \PW{x}{2}
      \SEMI
      \PR[\mRA]{x}{r}
      \SEMI
      \PW{y}{1}
      \\
      \hbox{\begin{tikzinline}[node distance=0.5em and 1.5em]
          \event{a}{\DW{x}{2}}{}
          \raevent{b}{\DR[\mRA]{x}{2}}{right=of a}
          \event{c}{\DW{y}{1}}{right=of b}
          \rf{a}{b}
        \end{tikzinline}}  
    \end{gathered}  
  \end{align*}
\end{example}

@@

\begin{example}
  Revisiting \refex{ex:rrd1} and eliding irrelevant transformers:
  \begin{align*}
    \begin{gathered}[t]
      \PR{y}{r}
      \\
      \hbox{\begin{tikzinline}[node distance=0.5em and .5em]
          \event{b}{\DR{y}{1}}{}
          \xform{x1i}{\RW\limplies\bForm}{right=of b} %x1d}
        \end{tikzinline}}  
    \end{gathered}  
    &&
    \begin{gathered}[t]
      \IF{r}\THEN s\GETS x\FI
      \\
      \hbox{\begin{tikzinline}[node distance=0.5em and 1.5em]
          \event{c}{r\mid\DW{x}{0}}{}
          % \xform{x1d}{\bForm[\TRUE/\Dx{\aLoc}]}{below=of c}
          % \xform{x1i}{\lnot\Qw{y}\land\bForm[\TRUE/\Dx{y}]}{below=of x1d}
          % \xo{c}{x1d}
        \end{tikzinline}}  
    \end{gathered}  
  \end{align*}
  Composing sequentially:
  \begin{align*}
    \begin{gathered}[t]
      \PR{y}{r}
      \SEMI
      \IF{r}\THEN s\GETS x\FI
      \\
      \hbox{\begin{tikzinline}[node distance=0.5em and .5em]
          \event{b}{\DR{y}{1}}{}
          \event{c}{\RW\limplies r\mid\DW{x}{0}}{right=of b}
          %\xform{x1i}{\RW\limplies\bForm}{right=of b} %x1d}
        \end{tikzinline}}  
    \end{gathered}  
  \end{align*}
  Embedding the thread in thread group, we have, as desired:
  \begin{align*}
    \begin{gathered}[t]
      \PR{y}{r}
      \SEMI
      \IF{r}\THEN s\GETS x\FI
      \\
      \hbox{\begin{tikzinline}[node distance=0.5em and .5em]
          \event{b}{\DR{y}{1}}{}
          \event{c}{\FALSE\limplies r\mid\DW{x}{0}}{right=of b}
          %\xform{x1i}{\RW\limplies\bForm}{right=of b} %x1d}
        \end{tikzinline}}  
    \end{gathered}  
  \end{align*}
\end{example}

@@

\begin{definition}[$\xCO$/$\xRASC$/$\xDGR$/$\xRRD$]
  \label{def:pomsets-arm}
  Update \refdef{def:pomsets-trans} to:
  \begin{enumerate}
  \item[\ref{S3})]
    $\labelingForm(\aEv)$ implies $\QS{\aLoc}{\amode}\land\aExp{=}\aVal$,
  \item[\ref{L3})]
    $\labelingForm(\aEv)$ implies $\QL{\aLoc}{\amode}$.
  \item[\ref{T3})]
    $\labelingForm(\aEv)$ implies
    $\labelingForm_1(\aEv)[\TRUE/\Q{}][\TRUE/\RW]$ if $\labelingAct_1(\aEv)$ is a write,
    \\
    $\labelingForm(\aEv)$ implies
    $\labelingForm_1(\aEv)[\TRUE/\Q{}][\FALSE/\RW]$ otherwise.
  \end{enumerate}
  \begin{enumerate}
  \item[\ref{S4})]
    $\aTr{\bEvs}{\bForm}$ implies $(\Qw{\aLoc}\limplies\aExp{\neq}\aVal)\land \DS{\aLoc}{\amode}\bForm\noSUB{[\aExp/\aLoc]}$,
  \item[\ref{S5})]
    $\aTr{\cEvs}{\bForm}$ implies $\lnot\Qw{\aLoc}\land \DS{\aLoc}{\amode}\bForm\noSUB{[\aExp/\aLoc]}$.
  \item[\ref{L4})]
    $\aTr{\bEvs}{\bForm}$ implies $\aVal{=}\aReg\limplies\bForm$, 
  \item[\ref{L5})]
    % $\aTr{\cEvs}{\bForm}$ implies $\lnot\Qx{\aLoc} \land \DL{\aLoc}{\amode} \land(\RW\limplies(\aVal{=}\aReg\lor\aLoc{=}\aReg)\limplies\bForm)$,
    % \item[\ref{L6})]
    $\aTr{\cEvs}{\bForm}$ implies $\lnot\Qx{\aLoc} \land \DL{\aLoc}{\amode}{}
    \land (\RW\limplies\bForm)$.
  \end{enumerate}  
\end{definition}
